---
title: "Escaping social-ecological trap"
author: "Wang Zhuangzhuang"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Composite system state index

#### Observing six system state variables

```{r}
library(ggplot2)
library(cowplot)
library(readxl)

data = read_xlsx("Data for composite index.xlsx")
head(data)

#Observe change patterns of raw data
p1<-ggplot(data=data,aes(x=Year,y=Net_income))+
  geom_line()+geom_point()
p2<-ggplot(data=data,aes(x=Year,y=PerCAGrain))+
  geom_line()+geom_point()
p3<-ggplot(data=data,aes(x=Year,y=PerCAFruits))+
  geom_line()+geom_point()
p4<-ggplot(data=data,aes(x=Year,y=PerCAOil_crops))+
  geom_line()+geom_point()
p5<-ggplot(data=data,aes(x=Year,y=PerCACotton))+
  geom_line()+geom_point()
p6<-ggplot(data=data,aes(x=Year,y=Sediment_load))+
  geom_line()+geom_point()

plot_grid(p1,p2,p3,p4,p5,p6,nrow = 3,labels="AUTO",
          label_size = 9,align = "v")
```


#### Calculating composite state index using different methods

```{r}
library(Compind)
library(kableExtra)
library(readxl)

data = read_xlsx("Data for composite index.xlsx")

#Here we define the sediment load (represents soil erosion) as the negative variable to  social-ecological state, i.e., the higher the value, the more undesirable the system state. Per capita net income of rural household and per capita/area ecosystem goods (grain, fruits, oil-bearing crops, and cotton) are positive variables, i.e., the higher the value, the more desirable the system state.

#Normalize data using max-min method
#to avoid 0 and 1, we set the max normalized value as 0.996 and the min normalized value as 0.002
normalize_POS <- function(x) {
  return ((0.996 - 0.002)*(x - min(x))/(max(x)-min(x))+0.002)
}
normalize_NEG <- function(x) {
  return ((0.996-0.002)*(max(x)-x)/(max(x)-min(x))+0.002)
}

data_norm<-data.frame(normalize_POS(data[,2]),
                      normalize_POS(data[,3]),
                      normalize_POS(data[,4]),
                      normalize_POS(data[,5]),
                      normalize_POS(data[,6]),
                      normalize_NEG(data[,7]))
                      

#Calculating composite index (scores) using different methods
#details for different methods provided by compind package can be found in the following link: https://cran.r-project.org/web/packages/Compind/Compind.pdf

#Benefit of the Doubt approach (BoD): 'ci_bod' function
CI_BoD_estimated<-ci_bod(data_norm,indic_col = c(1:6))
ci_bod_est<-as.data.frame(CI_BoD_estimated$ci_bod_est)
names(ci_bod_est) <- "Benef_Doubt"
plot(ci_bod_est$Benef_Doubt,type="l")

#Constrained Benefit of the Doubt approach (BoD): 'ci_bod_constr' function
CI_BoD_constr_estimated<-ci_bod_constr(data_norm,indic_col = c(1:6),up_w=1,low_w=0)
ci_bod_constr_est<-as.data.frame(CI_BoD_constr_estimated$ci_bod_constr_est)
names(ci_bod_constr_est) <- "Cons_Benef_Doubt"
plot(ci_bod_constr_est$Cons_Benef_Doubt,type="l")

#Weighting method based on Factor AnalysisL: 'ci_factor' function
CI_Factor_estimated<-ci_factor(data_norm,indic_col = c(1:6),method="ALL")
ci_factor_est <- data.frame( CI_Factor_estimated$ci_factor_est)
names(ci_factor_est) <- "ci_factor"
plot(ci_factor_est$ci_factor,type="l")

#Generalized geometric mean quantity index numbers: 'ci_geom_gen' function
CI_Geom_gen_estimated<-ci_geom_gen(data_norm,indic_col = c(1:6),meth = "EQUAL")
ci_mean_geom_est<-data.frame(CI_Geom_gen_estimated$ci_mean_geom_est)
names(ci_mean_geom_est) <- "ci_mean_geom_est"
plot(ci_mean_geom_est$ci_mean_geom_est,type="l")

#MAZZIOTTA-PARETO INDEX (MPI): 'ci_mpi' function
CI_MPI_estimated <- ci_mpi(data_norm,indic_col = c(1:6))  
ci_mpi_est <- data.frame(CI_MPI_estimated$ci_mpi_est)
names(ci_mpi_est) <- "Mazziotta_Pareto"
plot(ci_mpi_est$Mazziotta_Pareto,type="l")

#Robust Benefit of the Doubt approach (RBOD): 'ci_rbod' function
CI_RBoD_estimated <-  ci_rbod(data_norm,indic_col = c(1:6),
                              M = 5,  #The number of elements in each sample.
                              B = 200) #The number of bootstap replicates.
ci_rbod_est <- data.frame(CI_RBoD_estimated$ci_rbod_est)
names(ci_rbod_est) <- "Benef_Doubt_Rob"
plot(ci_rbod_est$Benef_Doubt_Rob,type="l")

#WROCLAW TAXONOMY METHOD
#Note: units with higher values for the simple indicators get lower values of composite indicator
CI_wroclaw_estimated <-  ci_wroclaw(data_norm,indic_col = c(1:6))
ci_wroclaw_est <- data.frame( CI_wroclaw_estimated$ci_wroclaw_est)
names(ci_wroclaw_est) <- "Wroclaw"
plot(ci_mpi_est$Mazziotta_Pareto,type="l")


#column bind all the composite index 
all_com_ind <- cbind( #row.names(scores.this),
  ci_bod_est, # Benefit of the Doubt approach
  ci_bod_constr_est, # Constrained Benefit of the Doubt approach
  ci_factor_est, #Factor analysis componnents
  ci_mean_geom_est, # Generalized geometric mean quantity index numbers
  ci_mpi_est, # MAZZIOTTA-PARETO INDEX
  ci_rbod_est, # Robust Benefit of the Doubt approach
  ci_wroclaw_est) # WROCLAW TAXONOMY METHOD

kable(all_com_ind, caption = "Composite with different algorithm") %>%
           kable_styling(bootstrap_options = c("striped", "bordered", "condensed", "responsive"), font_size = 9)

#Observe change patterns of composite index
all_com_ind<-data.frame(data[,1],all_com_ind)
p1<-ggplot(data=all_com_ind,aes(x=Year,y=Benef_Doubt))+geom_line()+geom_point()
p2<-ggplot(data=all_com_ind,aes(x=Year,y=Cons_Benef_Doubt))+geom_line()+geom_point()
p3<-ggplot(data=all_com_ind,aes(x=Year,y=ci_factor))+geom_line()+geom_point()
p4<-ggplot(data=all_com_ind,aes(x=Year,y=ci_mean_geom_est))+geom_line()+geom_point()
p5<-ggplot(data=all_com_ind,aes(x=Year,y=Mazziotta_Pareto))+geom_line()+geom_point()
p6<-ggplot(data=all_com_ind,aes(x=Year,y=Benef_Doubt_Rob))+geom_line()+geom_point()
p7<-ggplot(data=all_com_ind,aes(x=Year,y=Wroclaw))+geom_line()+geom_point()
plot_grid(p1,p2,p3,p4,p5,p6,p7,nrow = 4,labels="AUTO",label_size = 9,align = "v")

#Normalize all the composite index again on a 0 to 1 scale in order to be compared.
normalize_POS_1 <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}
normalize_NEG_1 <- function(x) {
  return ((max(x) - x) / (max(x) - min(x)))
}

com_index_norm<-data.frame(normalize_POS_1(all_com_ind[,2]),normalize_POS_1(all_com_ind[,3]),normalize_POS_1(all_com_ind[,4]),normalize_POS_1(all_com_ind[,5]),normalize_POS_1(all_com_ind[,6]),normalize_POS_1(all_com_ind[,7]),normalize_NEG_1(all_com_ind[,8]))
names(com_index_norm)<-c("Benef_Doubt","Cons_Benef_Doubt","ci_factor","ci_mean_geom_est",
                         "Mazziotta_Pareto","Benef_Doubt_Rob","Wroclaw")

com_index_norm<-data.frame(data[,1],com_index_norm)
```

#### Drawing for seven calculated composite system state index 

```{r}
library(ggplot2)
library(eoffice)
library(reshape2)

com_index_norm_draw<-com_index_norm

com_index_norm_draw$Wroclaw<-com_index_norm_draw$Wroclaw + 6
com_index_norm_draw$Benef_Doubt_Rob<-com_index_norm_draw$Benef_Doubt_Rob + 5
com_index_norm_draw$Mazziotta_Pareto<-com_index_norm_draw$Mazziotta_Pareto + 4
com_index_norm_draw$ci_mean_geom_est<-com_index_norm_draw$ci_mean_geom_est + 3
com_index_norm_draw$ci_factor<-com_index_norm_draw$ci_factor + 2
com_index_norm_draw$Cons_Benef_Doubt<-com_index_norm_draw$Cons_Benef_Doubt + 1
com_index_norm_draw$Benef_Doubt<-com_index_norm_draw$Benef_Doubt
                   
# Draw
Fig.S1 <- ggplot(data = com_index_norm_draw,mapping = aes(x = Year))+
  scale_y_continuous(limits = c(0,7),
                     breaks = c(0.5,1.5,2.5,3.5,4.5,5.5,6.5),expand = c(0,0),
                     labels = c('Benef_Doubt','Cons_Benef_Doubt','ci_factor',
                                'ci_mean_geom_est','Mazziotta_Pareto','Benef_Doubt_Rob',
                                'Wroclaw'))+
  geom_hline(yintercept = 0.5,linetype = 'dashed',color = '#000000',size = 0.3)+
  geom_hline(yintercept = 1.5,linetype = 'dashed',color = '#000000',size = 0.3)+
  geom_hline(yintercept = 2.5,linetype = 'dashed',color = '#000000',size = 0.3)+
  geom_hline(yintercept = 3.5,linetype = 'dashed',color = '#000000',size = 0.3)+
  geom_hline(yintercept = 4.5,linetype = 'dashed',color = '#000000',size = 0.3)+
  geom_hline(yintercept = 5.5,linetype = 'dashed',color = '#000000',size = 0.3)+
  geom_hline(yintercept = 6.5,linetype = 'dashed',color = '#000000',size = 0.3)+
  geom_line(mapping = aes(y = Wroclaw),color = '#028501',size = 0.8)+
  geom_line(mapping = aes(y = Benef_Doubt_Rob),color = '#009985',size = 0.8)+
  geom_line(mapping = aes(y = Mazziotta_Pareto),color = '#7ed4c9',size = 0.8)+
  geom_line(mapping = aes(y = ci_mean_geom_est),color = '#ffc653',size = 0.8)+
  geom_line(mapping = aes(y = ci_factor),color = '#f3f14e',size = 0.8)+
  geom_line(mapping = aes(y = Cons_Benef_Doubt),color = '#97afeb',size = 0.8)+
  geom_line(mapping = aes(y = Benef_Doubt),color = '#6584df',size = 0.8)+
  xlab('Year')+
  ylab('Methods')+
  theme_custom()+
  theme(aspect.ratio = 8/4)

Fig.S1

#topptx(Fig.S1,filename = "Composite system state index.pptx")
```

#### Breakpoints of composite system state index

```{r}
#define function for calculating standard error
st.err <- function(x){
  sd(x)/sqrt(length(x))
}
mean<-apply(com_index_norm[,c(2:8)],1,mean)
se<-apply(com_index_norm[,c(2:8)],1,st.err)
data.draw<-data.frame(data[,1],mean,se)

library(bfast)
timeseries<-ts(mean,start = 1949)
#Because social-ecological systems tend to maintain the same structure and state over a long period of time, we try to delineate the period as large as possible and at the same time they are robust to the set h parameter in the bfast function.
breakpoints1<-bfast(timeseries, h=0.2,season="none",max.iter=1)
breakpoints2<-bfast(timeseries, h=0.3,season="none",max.iter=1)
breakpoints3<-bfast(timeseries, h=0.4,season="none",max.iter=1)

breakpoints1 #breakpoint 1981 2003
breakpoints2 #breakpoint 1981
breakpoints3 #breakpoint 1981

plot(breakpoints1)
plot(breakpoints2)
plot(breakpoints3)

#when h>=0.3 the The results of the breakpoint calculation start to converge
#We identified the final two breakpoint 1981 and 2003 and divided three periods: 1949-1981, 1981-2003, and 2003-2020
#The three periods have different changes features

#combine data
#data.draw<-data.frame(data.draw,breakpoints1$output[[1]]$Tt)
#calculating mean value according to breakpoints
mean_p1<-mean(data.draw[c(1:33),2])
mean_p2<-mean(data.draw[c(34:55),2])
mean_p3<-mean(data.draw[c(56:72),2])
mean_value<-c(rep(mean_p1,times=33),rep(mean_p2,times=22),rep(mean_p3,times=17))
data.draw<-data.frame(data.draw[,1:3],mean_value)

colnames(data.draw)<-c("Year","mean","se","mean_period")
```

#### Drawing for composite system state index

composite system state mean value ± se and fitted trend by bfast package

```{r}
library(ggplot2)
library(eoffice)
library(RColorBrewer)

##====theme function====##
theme_custom <- function(){
  myTheme <- theme(panel.background = element_rect(fill = 'white',color = 'black',size = 0.5),
                   panel.grid = element_blank(),
                   legend.position = 'none',
                   plot.margin = margin(5,5,3,3),
                   plot.background = element_blank(),
                   axis.ticks = element_line(size = 0.2),
                   axis.ticks.length = unit(0.15,'lines'),
                   axis.title.y = element_text(size = 10.5,margin = margin(0,3,0,0),face = 'bold',family = 'Times'),
                   axis.title.x = element_text(size = 10.5,margin = margin(4,0,0,0),face = 'bold',family = 'Times'),
                   axis.text.y = element_text(size = 9,margin = margin(0,6,0,0),family = 'Times',color = '#000000'),
                   axis.text.x = element_text(size = 9,margin = margin(8,0,0,0),family = 'Times',color = '#000000'))
  return(myTheme)
}
##====theme function====##

cssi_plot<-ggplot(data.draw,aes(x=Year, y=mean))+
  annotate("rect",xmin=-Inf, xmax=1981, ymin=-Inf, ymax=Inf,fill='#E7DAD2',alpha = 0.7)+
  annotate("rect",xmin=2003, xmax=Inf, ymin=-Inf, ymax=Inf,fill='#8ECFC9',alpha = 0.7)+
  #geom_vline(xintercept=c(1981,2003),lty=5)+ 
  geom_line(aes(y=mean),size=0.75,color= rgb(157,158,162,max = 255)) +
  geom_point(aes(y=mean),size=2,shape=21,color="black",fill="#1e56a0")+
  geom_line(aes(y=mean_period),lty=5,colour="red")+
  #geom_errorbar(aes(ymin=mean-se, ymax=mean+se),colour="black", width=.03,size=0.75)+
  geom_ribbon(aes(ymin=mean-se,ymax=mean+se),alpha=0.2,fill="#1e56a0"
              )+ #color="black",linetype="dotted"
  labs(x="Year",y="Composite system state index")+
  #theme_custom()+
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        aspect.ratio =7.5/10)
  #theme(aspect.ratio = 6.18/10)

cssi_plot

#topptx(cssi_plot,filename = "cssi_plot.pptx")
```


## Social-ecological network

#### Calculating mutual information between system elements

```{r}

library(readxl)
library(infotheo) #provide 'mutinformation' function
library(minet)
#library(arules) #provide discretize function

data_ele = read_xlsx("Data for mutual information.xlsx")
#read_excel("Data for mutual information.xlsx",sheet="table1")
head(data_ele)

data_p1<-data_ele[c(1:33),c(2:21)] #1949-1981
data_p2<-data_ele[c(33:55),c(2:21)] #1981-2003
data_p3<-data_ele[c(55:72),c(2:21)] #1982-2020

#calculating mutual information
#First, discretizes data using the equal frequencies or equal width binning algorithm.
nbins_p1<- sqrt(NROW(data_p1))
nbins_p2<- sqrt(NROW(data_p2))
nbins_p3<- sqrt(NROW(data_p3))
data_p1_dis<-infotheo::discretize(data_p1,"equalfreq", nbins_p1)
data_p2_dis<-infotheo::discretize(data_p2,"equalfreq", nbins_p2)
data_p3_dis<-infotheo::discretize(data_p3,"equalfreq", nbins_p3)

MI_p1<-minet(data_p1_dis,method = "mrnet",estimator = "mi.shrink",disc = "none")
MI_p2<-minet(data_p2_dis,method = "mrnet",estimator = "mi.shrink",disc = "none")
MI_p3<-minet(data_p3_dis,method = "mrnet",estimator = "mi.shrink",disc = "none")

#display matrix using heatmap
palf <- colorRampPalette(c("gold", "dark orange"))
heatmap(MI_p1[,1:20],Rowv = NA, Colv = NA, col = palf(100),
scale="none", margins=c(10,10))
heatmap(MI_p2[,1:20],Rowv = NA, Colv = NA, col = palf(100),
scale="none", margins=c(10,10))
heatmap(MI_p3[,1:20],Rowv = NA, Colv = NA, col = palf(100),
scale="none", margins=c(10,10))
```

#### Constructing mutual information network using igraph package

```{r}
library(igraph)
library(ggraph)
library(RColorBrewer)

net.1<-graph_from_adjacency_matrix(MI_p1,mode=c("undirected"),
                                   diag = FALSE,
                                   weighted =TRUE,
                                   add.rownames="name")
net.2<-graph_from_adjacency_matrix(MI_p2,mode=c("undirected"),
                                   diag = FALSE,
                                   weighted =TRUE,
                                   add.rownames="name")
net.3<-graph_from_adjacency_matrix(MI_p3,mode=c("undirected"),
                                   diag = FALSE,
                                   weighted =TRUE,
                                   add.rownames="name")

#We classified social-ecological elements into the following types:
#1        Rural_pop       Socio-economic factor
#2       Urban_rate       Socio-economic factor
#3       Net_income       Socio-economic factor
#4     Liveli_diver       Socio-economic factor
#5   Sow_area_grain       Agricultural inputs
#6    Area_orchards       Agricultural inputs
#7     Sow_area_oil       Agricultural inputs
#8  Sow_area_cotton       Agricultural inputs
#9      Irriga_area       Agricultural inputs
#10      Fertil_use       Agricultural inputs
#11   Agri_mach_pow       Agricultural inputs
#12    Output_grain       Agricultural outputs
#13   Output_fruits       Agricultural outputs
#14      Output_oil       Agricultural outputs
#15   Output_cotton       Agricultural outputs
#16      Affor_area       Ecological restoration
#17  Planting_trees       Ecological restoration
#18        Sed_load       Environment condition
#19             Pre       Climate
#20             Tem       Climate
V(net.1)$type<-c(rep("Socio-economic factor",4),
             rep("Agricultural inputs",7),
             rep("Agricultural outputs",4),
             rep("Ecological restoration",2),
             rep("Environment condition",1),
             rep("Climate",2))
V(net.2)$type<-c(rep("Socio-economic factor",4),
             rep("Agricultural inputs",7),
             rep("Agricultural outputs",4),
             rep("Ecological restoration",2),
             rep("Environment condition",1),
             rep("Climate",2))
V(net.3)$type<-c(rep("Socio-economic factor",4),
             rep("Agricultural inputs",7),
             rep("Agricultural outputs",4),
             rep("Ecological restoration",2),
             rep("Environment condition",1),
             rep("Climate",2))

V(net.1)$type.num<-as.numeric(as.factor(V(net.1)$type))
V(net.2)$type.num<-as.numeric(as.factor(V(net.2)$type))
V(net.3)$type.num<-as.numeric(as.factor(V(net.3)$type))

display.brewer.all()
display.brewer.pal(6, "Set1")
display.brewer.pal(6, "Set2")
display.brewer.pal(6, "Set3")
display.brewer.pal(6, "Pastel2")
display.brewer.pal(6, "Pastel1")
display.brewer.pal(6, "Paired")
display.brewer.pal(6, "Dark2")
display.brewer.pal(6, "Accent")


colrs <- brewer.pal(6, "Accent") #Paired Dark2
V(net.1)$color <- colrs[V(net.1)$type.num]
V(net.2)$color <- colrs[V(net.2)$type.num]
V(net.3)$color <- colrs[V(net.3)$type.num]

plot(net.1)
plot(net.2)
plot(net.3)
```

#### Analyzing and drawing network structure

```{r}
library(igraph)
library(netdiffuseR) #rescale_vertex_igraph

# Community detection (by optimizing modularity over partitions):
clp.1 <- cluster_optimal(net.1,weights = E(net.1)$weight)
clp.2 <- cluster_optimal(net.2,weights = E(net.2)$weight)
clp.3 <- cluster_optimal(net.3,weights = E(net.3)$weight)

V(net.1)$community <- clp.1$membership
V(net.2)$community <- clp.2$membership
V(net.3)$community <- clp.3$membership


#Find Eigenvector Centrality Scores of Network Positions
evcent.1<-evcent(net.1,scale = T)
evcent.2<-evcent(net.2,scale = T)
evcent.3<-evcent(net.3,scale = T)

V(net.1)$size3 <- evcent.1$vector
V(net.2)$size3 <- evcent.2$vector
V(net.3)$size3 <- evcent.3$vector

# Based the weigh (Normalized mutual information), We classified the edge width into five classes:
# 0-0.2 0.2-0.4 0.4-0.6 0.6-0.8 0.8-1 for visualization of network and making ledged

# weight breaks
weight_breaks <- c(0,0.2,0.4,0.6,0.8,1)
weight_cut.1<-cut(E(net.1)$weight, breaks = weight_breaks, include.lowest = TRUE)
weight_cut.2<-cut(E(net.2)$weight, breaks = weight_breaks, include.lowest = TRUE)
weight_cut.3<-cut(E(net.3)$weight, breaks = weight_breaks, include.lowest = TRUE)

width.1<-as.numeric(weight_cut.1)
width.2<-as.numeric(weight_cut.2)
width.3<-as.numeric(weight_cut.3)

library(plyr)
width.1<-mapvalues(width.1, c("1","2","3","4","5"),c("1","4","6","8","11"))
width.2<-mapvalues(width.2, c("1","2","3","4","5"),c("1","4","6","8","11"))
width.3<-mapvalues(width.3, c("1","2","3","4","5"),c("1","4","6","8","11"))

E(net.1)$width<-width.1
E(net.2)$width<-width.2
E(net.3)$width<-width.3
```

```{r}
library(eoffice)
library(ggplotify)
#topptx(filename = "test.pptx")

#set colors
node.col<-grDevices::adjustcolor(c("tomato","gold","#C5E5E7","#ECD89A","#557799"), alpha=1) #"#ECD89A"
mark.col<-grDevices::adjustcolor(c("tomato","gold","#C5E5E7","#ECD89A","#557799"), alpha=0.4)
mark.bor<-grDevices::adjustcolor(c("tomato","gold","#C5E5E7","#ECD89A","#557799"), alpha=0.8)

par(bg="#f5f5f2")
set.seed(2)
plot(net.1, 
     vertex.size=rescale_vertex_igraph(V(net.1)$size3,
                                       par.usr = par("usr"),
                                       minmax.relative.size = getOption("diffnet.minmax.relative.size", c(0.01, 0.04)),
                                       adjust = 500),
     vertex.color=node.col[V(net.1)$community],
     vertex.label.color="black",
     vertex.label.font = 2,
     vertex.label.cex=1,
     edge.width=E(net.1)$width,
     label.font=2,label.cex=10,
     layout=layout_with_fr, 
     mark.groups=clp.1,
     mark.shape = 1/2,
     mark.col=mark.col,
     mark.border = mark.bor,
     mark.expand = 15)

#topptx(filename = "network.p1.pptx")
```

```{r}
par(bg="#f5f5f2")
set.seed(6)
plot(net.2, 
     vertex.size=rescale_vertex_igraph(V(net.2)$size3,
                                       par.usr = par("usr"),
                                       minmax.relative.size = getOption("diffnet.minmax.relative.size", c(0.01, 0.04)),
                                       adjust = 500),
     vertex.color=node.col[V(net.2)$community],
     vertex.label.color="black",
     vertex.label.font = 2,
     vertex.label.cex=1,
     edge.width=E(net.2)$width,
     label.font=2,label.cex=10,
     layout=layout_with_fr, 
     mark.groups=clp.2,
     mark.shape = 1/2,
     mark.col=mark.col,
     mark.border = mark.bor,
     mark.expand = 15)

#topptx(filename = "network.p2.pptx")
```

```{r}
par(bg="#f5f5f2")
set.seed(5)
plot(net.3, 
     vertex.size=rescale_vertex_igraph(V(net.3)$size3,
                                       par.usr = par("usr"),
                                       minmax.relative.size = getOption("diffnet.minmax.relative.size", c(0.01, 0.04)),
                                       adjust = 500),
     vertex.color=node.col[V(net.3)$community],
     vertex.label.color="black",
     vertex.label.font = 2,
     vertex.label.cex=1,
     edge.width=E(net.3)$width,
     label.font=2,label.cex=10,
     layout=layout_with_fr, 
     mark.groups=clp.3,
     mark.shape = 1/2,
     mark.col=mark.col,
     mark.border = mark.bor,
     mark.expand = 15)

#topptx(filename = "network.p3.pptx")
```


```{r}
library(reshape2)
library(ggsci)
##====theme function====##
theme_custom <- function(){
  myTheme <- theme(panel.background = element_rect(fill = 'white',color = 'black',size = 0.5),
                   panel.grid = element_blank(),
                   legend.position = 'right',
                   plot.margin = margin(5,5,3,3),
                   plot.background = element_blank(),
                   axis.ticks = element_line(size = 0.2),
                   axis.ticks.length = unit(0.15,'lines'),
                   axis.title.y = element_text(size = 10.5,margin = margin(0,3,0,0),face = 'bold',family = 'Times'),
                   axis.title.x = element_text(size = 10.5,margin = margin(4,0,0,0),face = 'bold',family = 'Times'),
                   axis.text.y = element_text(size = 9,margin = margin(0,6,0,0),family = 'Times',color = '#000000'),
                   axis.text.x = element_text(size = 9,margin = margin(8,0,0,0),family = 'Times',color = '#000000'))
  return(myTheme)
}
##====theme function====##

##====prepare data====##
node.evcent<-data.frame(evcent.1$vector,evcent.2$vector,evcent.3$vector)
colnames(node.evcent)<-c("evcent.p1","evcent.p2","evcent.p3")
node.evcent$elements<-rownames(node.evcent)
rownames(node.evcent)<-NULL
node.evcent<-node.evcent[,c(4,1:3)]
#prepare for drawing data
node.evcent<-melt(node.evcent)
##====prepare data====##

##====draw====##
plot.node.evcent<-ggplot(node.evcent, aes(x=elements, y=value, fill=variable)) +
  geom_bar(stat="identity", position=position_dodge(),color="black", width=.6) +
  #scale_fill_npg()+
  #scale_fill_aaas()+
  scale_fill_simpsons()+
  coord_flip()+
  xlab("Network nodes")+ylab("Normalized eigenvector centrality scores")+
  theme_custom()+
  theme(aspect.ratio = 9/4)

plot.node.evcent
#topptx(plot.node.evcent,filename = "plot.node.evcent.pptx")
```

#### Comprehensively drawing for social-ecological elements


```{r}
library(export)
library(readxl)
library(ggplot2)
library(dplyr)
library(patchwork) # To display 2 charts together
library(hrbrthemes)
library(cowplot)
library(eoffice)

data_elements = read_xlsx("Drawing social-ecological elements.xlsx")
head(data_elements)

p1<-ggplot(data=data_elements) +
  annotate("rect",xmin=-Inf, xmax=1981, ymin=-Inf, ymax=Inf,fill='#E7DAD2',alpha = 0.7)+
  annotate("rect",xmin=2003, xmax=Inf, ymin=-Inf, ymax=Inf,fill='#8ECFC9',alpha = 0.7)+
  geom_line(aes(x=Year, y = `Total population`), color='grey70',size=1)+
  geom_line(aes(x=Year, y=Rural_pop),color="#3fbac2", size=1) +
  geom_line(aes(x=Year, y=`Urban people`),color="#e95280", size=1) +
  labs(x="Year",y="Population")+
  #geom_vline(xintercept=c(1981,2003),lty=5)+
  #ggtitle("Temperature: range 1-10") +
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        aspect.ratio = 5/5)


p2<-ggplot(data=data_elements) +
  annotate("rect",xmin=-Inf, xmax=1981, ymin=-Inf, ymax=Inf,fill='#E7DAD2',alpha = 0.7)+
  annotate("rect",xmin=2003, xmax=Inf, ymin=-Inf, ymax=Inf,fill='#8ECFC9',alpha = 0.7)+
  geom_line(aes(x=Year, y=Urban_rate),color="#e95280", size=1) +
  labs(x="Year",y="Urbanization rate")+
  #geom_vline(xintercept=c(1981,2003),lty=5)+
  #ggtitle("Temperature: range 1-10") +
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        aspect.ratio = 5/5)

p3<-ggplot(data=data_elements) +
  annotate("rect",xmin=-Inf, xmax=1981, ymin=-Inf, ymax=Inf,fill='#E7DAD2',alpha = 0.7)+
  annotate("rect",xmin=2003, xmax=Inf, ymin=-Inf, ymax=Inf,fill='#8ECFC9',alpha = 0.7)+
  geom_line(aes(x=Year, y=Net_income),color="#e95280", size=1) +
  labs(x="Year",y="Net_income")+
  #geom_vline(xintercept=c(1981,2003),lty=5)+
  #ggtitle("Temperature: range 1-10") +
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        aspect.ratio = 5/5)

p4<-ggplot(data=data_elements) +
  annotate("rect",xmin=-Inf, xmax=1981, ymin=-Inf, ymax=Inf,fill='#E7DAD2',alpha = 0.7)+
  annotate("rect",xmin=2003, xmax=Inf, ymin=-Inf, ymax=Inf,fill='#8ECFC9',alpha = 0.7)+
  geom_line(aes(x=Year, y=`Engel's_coe_rural_res`),color="#e95280", size=1) +
  labs(x="Year",y="Engel's_coe_rural_res")+
  #geom_vline(xintercept=c(1981,2003),lty=5)+
  #ggtitle("Temperature: range 1-10") +
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        aspect.ratio = 5/5)


p5<-ggplot(data=data_elements) +
  geom_area(aes(x=Year, y = Sow_area_grain), fill='#1e56a0',alpha = 0.3)+
  geom_area(aes(x=Year, y = Area_orchards), fill='#1687a7',alpha = 0.5)+
  geom_area(aes(x=Year, y = Sow_area_oil), fill='#ffb400',alpha = 0.5)+
  geom_area(aes(x=Year, y = Sow_area_cotton), fill='#e95280',alpha = 0.5)+
  #geom_vline(xintercept=c(1981,2003),lty=5)+
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        legend.position = 'left',
        aspect.ratio = 5/5)

p6<-ggplot(data=data_elements) +
  annotate("rect",xmin=-Inf, xmax=1981, ymin=-Inf, ymax=Inf,fill='#E7DAD2',alpha = 0.7)+
  annotate("rect",xmin=2003, xmax=Inf, ymin=-Inf, ymax=Inf,fill='#8ECFC9',alpha = 0.7)+
  geom_line(aes(x=Year, y=`Grain (10000t)`),color="#1e56a0", size=1) +
  geom_line(aes(x=Year, y=`Fruits(10000t)`),color="#1687a7", size=1) +
  geom_line(aes(x=Year, y=`Oil_crops(10000t)`),color="#ffb400", size=1) +
  geom_line(aes(x=Year, y=`Cotton(10000t)`),color="#e95280", size=1) +
  #geom_vline(xintercept=c(1981,2003),lty=5)+
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        aspect.ratio = 5/5)


p7<-ggplot(data=data_elements) +
  annotate("rect",xmin=-Inf, xmax=1981, ymin=-Inf, ymax=Inf,fill='#E7DAD2',alpha = 0.7)+
  annotate("rect",xmin=2003, xmax=Inf, ymin=-Inf, ymax=Inf,fill='#8ECFC9',alpha = 0.7)+
  geom_line(aes(x=Year, y=PercGrain),color="#1e56a0", size=1) +
  geom_line(aes(x=Year, y=PercFruits),color="#1687a7", size=1) +
  geom_line(aes(x=Year, y=PercOil_crops),color="#ffb400", size=1) +
  geom_line(aes(x=Year, y=PercCotton),color="#e95280", size=1) +
  #geom_vline(xintercept=c(1981,2003),lty=5)+
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        aspect.ratio = 5/5)


p8<-ggplot(data=data_elements) +
  annotate("rect",xmin=-Inf, xmax=1981, ymin=-Inf, ymax=Inf,fill='#E7DAD2',alpha = 0.7)+
  annotate("rect",xmin=2003, xmax=Inf, ymin=-Inf, ymax=Inf,fill='#8ECFC9',alpha = 0.7)+
  geom_line(aes(x=Year, y=PeraGrain),color="#1e56a0", size=1) +
  geom_line(aes(x=Year, y=PeraOil_crops),color="#ffb400", size=1) +
  geom_line(aes(x=Year, y=PeraCotton),color="#e95280", size=1) +
  #geom_vline(xintercept=c(1981,2003),lty=5)+
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        aspect.ratio = 5/5)

p9<-ggplot(data=data_elements) +
  annotate("rect",xmin=-Inf, xmax=1981, ymin=-Inf, ymax=Inf,fill='#E7DAD2',alpha = 0.7)+
  annotate("rect",xmin=2003, xmax=Inf, ymin=-Inf, ymax=Inf,fill='#8ECFC9',alpha = 0.7)+
  geom_line(aes(x=Year, y=Agri_mach_pow),color="#e95280", size=1) +
  labs(x="Year",y="Agri_mach_pow")+
  #geom_vline(xintercept=c(1981,2003),lty=5)+
  #ggtitle("Temperature: range 1-10") +
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        aspect.ratio = 5/5)

p10<-ggplot(data=data_elements) +
  annotate("rect",xmin=-Inf, xmax=1981, ymin=-Inf, ymax=Inf,fill='#E7DAD2',alpha = 0.7)+
  annotate("rect",xmin=2003, xmax=Inf, ymin=-Inf, ymax=Inf,fill='#8ECFC9',alpha = 0.7)+
  geom_line(aes(x=Year, y=Fertil_use),color="#e95280", size=1) +
  labs(x="Year",y="Fertil_use")+
  #geom_vline(xintercept=c(1981,2003),lty=5)+
  #ggtitle("Temperature: range 1-10") +
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        aspect.ratio = 5/5)

p11<-ggplot(data=data_elements) +
  annotate("rect",xmin=-Inf, xmax=1981, ymin=-Inf, ymax=Inf,fill='#E7DAD2',alpha = 0.7)+
  annotate("rect",xmin=2003, xmax=Inf, ymin=-Inf, ymax=Inf,fill='#8ECFC9',alpha = 0.7)+
  geom_line(aes(x=Year, y=Irriga_area),color="#e95280", size=1) +
  labs(x="Year",y="Irriga_area")+
  #geom_vline(xintercept=c(1981,2003),lty=5)+
  #ggtitle("Temperature: range 1-10") +
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        aspect.ratio = 5/5)

p12<-ggplot(data=data_elements) +
  annotate("rect",xmin=-Inf, xmax=1981, ymin=-Inf, ymax=Inf,fill='#E7DAD2',alpha = 0.7)+
  annotate("rect",xmin=2003, xmax=Inf, ymin=-Inf, ymax=Inf,fill='#8ECFC9',alpha = 0.7)+
  geom_line(aes(x=Year, y=Affor_area),color="#e95280", size=1) +
  labs(x="Year",y="Affor_area")+
  #geom_vline(xintercept=c(1981,2003),lty=5)+
  #ggtitle("Temperature: range 1-10") +
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        aspect.ratio = 5/5)

p13<-ggplot(data=data_elements) +
  annotate("rect",xmin=-Inf, xmax=1981, ymin=-Inf, ymax=Inf,fill='#E7DAD2',alpha = 0.7)+
  annotate("rect",xmin=2003, xmax=Inf, ymin=-Inf, ymax=Inf,fill='#8ECFC9',alpha = 0.7)+
  geom_line(aes(x=Year, y=Pre),color="#e95280", size=1) +
  labs(x="Year",y="Pre")+
  #geom_vline(xintercept=c(1981,2003),lty=5)+
  #ggtitle("Temperature: range 1-10") +
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        aspect.ratio = 5/5)

p14<-ggplot(data=data_elements) +
  annotate("rect",xmin=-Inf, xmax=1981, ymin=-Inf, ymax=Inf,fill='#E7DAD2',alpha = 0.7)+
  annotate("rect",xmin=2003, xmax=Inf, ymin=-Inf, ymax=Inf,fill='#8ECFC9',alpha = 0.7)+
  geom_line(aes(x=Year, y=Tem),color="#e95280", size=1) +
  labs(x="Year",y="Tem")+
  #geom_vline(xintercept=c(1981,2003),lty=5)+
  #ggtitle("Temperature: range 1-10") +
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        aspect.ratio = 5/5)

p15<-ggplot(data=data_elements) +
  annotate("rect",xmin=-Inf, xmax=1981, ymin=-Inf, ymax=Inf,fill='#E7DAD2',alpha = 0.7)+
  annotate("rect",xmin=2003, xmax=Inf, ymin=-Inf, ymax=Inf,fill='#8ECFC9',alpha = 0.7)+
  geom_line(aes(x=Year, y=Sediment_load),color="#e95280", size=1) +
  labs(x="Year",y="Sediment_load")+
  #geom_vline(xintercept=c(1981,2003),lty=5)+
  #ggtitle("Temperature: range 1-10") +
  theme(panel.background = element_blank(),
        panel.grid.major =element_blank(),
        panel.grid.major.y=element_line(color = "grey30",size = 0.5,linetype = 2),
        axis.line.x = element_line(colour = "black",size = 0.8),
        axis.text = element_text(face="bold", color="black", 
                           size=11),
        panel.border = element_blank(),
        aspect.ratio = 5/5)

plot_grid(p1,p2,p3,p4,p5,p6,p7,p8,
          p9,p10,p11,p12,p13,p14,p15,
          nrow = 4,
          labels="AUTO",
          label_size = 8,
          align = "v")

#topptx(file="social_ecological elements.pptx",width = 13,height = 13)

```






















